Recruiting Chapter

### 2021-06-14 text/tables_figures_june_2021.Rmd
update 1-mode tables

kable(table_1mode_pubu$onemode_df, caption = 'Public universities count matrix') %>%
  kable_styling(latex_options = 'scale_down') %>%
  column_spec(c(1, 15), width = '8.5em') %>% 
  column_spec(2:13, width = '7em') %>% 
  column_spec(c(14, 16), width = '6em')

kable(table_1mode_pubu$onemode_pct_df, caption = 'Public universities percent matrix') %>%
  kable_styling(latex_options = 'scale_down') %>%
  column_spec(c(1, 15), width = '8.5em') %>% 
  column_spec(2:13, width = '7em') %>% 
  column_spec(c(14, 16), width = '6em')

@@

kable(table_1mode_privu$onemode_df, caption = 'Private universities count matrix') %>%
  kable_styling(latex_options = 'scale_down') %>%
  column_spec(1, width = '8.5em') %>%
  column_spec(2:15, width = '7em') %>% 
  column_spec(c(4:6, 10, 12, 13), width = '6em')

kable(table_1mode_privu$onemode_pct_df, caption = 'Private universities percent matrix') %>%
  kable_styling(latex_options = 'scale_down') %>%
  column_spec(1, width = '8.5em') %>%
  column_spec(2:15, width = '7em') %>% 
  column_spec(c(4:6, 10, 12, 13), width = '6em')

>>>>

kable(table_1mode_pubu$onemode_df, caption = 'Public universities count matrix') %>%
  kable_styling(latex_options = 'scale_down') %>%
  column_spec(c(1, 14), width = '8.5em') %>% 
  column_spec(2:13, width = '7em') %>% 
  column_spec(c(15, 16), width = '6em')

kable(table_1mode_pubu$onemode_pct_df, caption = 'Public universities percent matrix') %>%
  kable_styling(latex_options = 'scale_down') %>%
  column_spec(c(1, 14), width = '8.5em') %>% 
  column_spec(2:13, width = '7em') %>% 
  column_spec(c(15, 16), width = '6em')

@@

kable(table_1mode_privu$onemode_df, caption = 'Private universities count matrix') %>%
  kable_styling(latex_options = 'scale_down') %>%
  column_spec(c(1, 14, 15), width = '8.5em') %>%
  column_spec(2:11, width = '7em') %>% 
  column_spec(c(4:6, 10, 12, 13), width = '6em')

kable(table_1mode_privu$onemode_pct_df, caption = 'Private universities percent matrix') %>%
  kable_styling(latex_options = 'scale_down') %>%
  column_spec(c(1, 14, 15), width = '8.5em') %>%
  column_spec(2:11, width = '7em') %>% 
  column_spec(c(4:6, 10, 12, 13), width = '6em')
